\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-04-27 doc/publications/plos16/supplementary_information.tex

>>>>

SNP	Pvalue	Name	PaulPVALUE	RF
rs9969672	0.0323	TNFRSF11B	1.30E-05	1
rs62259232	0.0022	CTNNB1	4.12E-06	2
rs112558362	0.0003	rs112558362	9.90E-07	3
rs12563939	0.9795	ZBTB40	6.69E-07	4
rs6961378	0.0179	LINC0106	8.92E-06	5
rs1054629	0.5631	IBSP	8.62E-05	6
rs6894139	0.5229	MEF2C	6.92E-08	7
rs17195090	0.0643	rs17195090	1.80E-05	8
rs17743906	??	PRODH	1.21E-06	9
